Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-03-07 demystify.tex
updates

It is understandable that some students might feel uncomfortable mentioning this in fear that they lost a chance of working with a prof who might be biased against URM students.  However, if a prof. has such an issue, then you might not want to work with them anyway (and it is likely that the university would not tolerate such behavior). In my experience, it is the opposite: many profs. are actively looking for URM students to work with, and mentioning this in your application can help you stand out.

In addition to being aware of the importance of diversity and inclusion and want to contribute to it, profs. have incentives to work with URM students. For example, professors often seek grants from government sponsors such as NSF, which strongly encourage broadening participation in STEM (e.g., see \href{https://new.nsf.gov/cise/broadening-participation}{here} and \href{https://www.nsf.gov/pubs/2022/nsf22125/nsf22125.jsp}{here}). Prof. can also apply for grants from organizations and private donors, which have specific programs for URM students.  Thus, having URM students in their group can help them get these grants.

>>>>

It is understandable that some students might feel uncomfortable mentioning this in fear that they lost a chance of working with a faculty who might be biased against URM students.  However, if someone has such an issue, then you might not want to work with them anyway (and it is likely that the university would not tolerate such behavior). In my experience, it is the opposite: many profs. are actively looking for URM students to work with, and mentioning this in your application can help you stand out.

In addition to being aware of the importance of diversity and inclusion and want to contribute to it, profs. have incentives to work with URM students. For example, we often seek grants from government sponsors such as NSF, which strongly encourage broadening participation in STEM (e.g., see \href{https://new.nsf.gov/cise/broadening-participation}{here} and \href{https://www.nsf.gov/pubs/2022/nsf22125/nsf22125.jsp}{here}).
Also, sometimes providing this information can make it easier for faculty to apply for certain scholarships or fellowships to support you, e.g., from a private donor that has offered a fellowship only to students from certain background.
